paper_data

### 2023-08-18 paper_data.Rmd
some review

## Original LMF data set to LMF subset

Fetch Netherlands boundaries from RIVM GIS server

```{r}
conn <- dbConnect(PostgreSQL(), dbname="geodata", user = "ro", password="ro!geo", host = "geodatabase.rivm.nl")
NL <- st_read(conn, query = "SELECT * FROM nl.adm_wijkbuurt_2022_gen;") %>%
  filter(indeling == 'gemeente') %>% st_union()
st_write(NL, "data_paper/NL.shp", append=F)
```

@@

```{r}
# Abiotic measurements for LMF data 
LMF.dir <- file.path('LMF', 'LMF data.xlsx')
df.abiotic <- read_excel(LMF.dir, 1)[-1,-1] %>% distinct(releve_nr, .keep_all=T) %>% 
  mutate(across(DATE:`N-(NO3+NO2)`,as.numeric)) %>% mutate(NAAM=tolower(str_replace_all(NAAM, " ", "")))
# Fix some identifier names in abiotic data
naam <- df.abiotic$NAAM
# some FR**** and FR**** identifiers were not properly zero padded
replace.index <- substr(naam,1,2) %in% c("fr", "fl")
pad.4 <- paste(substr(naam,1,2), str_pad(substr(naam,3,nchar(naam)), 4, pad="0"), sep="")
df.abiotic[replace.index, "NAAM"] <- pad.4[replace.index]
# Some GR**** identifiers were GR****/GR****
replace.index <- grepl('/', df.abiotic$NAAM, fixed = TRUE)
last.6 <- substr(naam, nchar(naam)-6+1, nchar(naam))
df.abiotic[replace.index, "NAAM"] <- last.6[replace.index]
# Lisa's fixes to coordinates 
# Tostrams, Lisa <lisa.tostrams@rivm.nl>
df.abiotic.2 <- read.csv('LMF/lmf_log_data_corrected_coords.csv') %>% 
  distinct(releve_nr, .keep_all=T) %>% 
  select(releve_nr, `X.coördinaat`, `Y.coördinaat`)
# Replace coordinates
df.abiotic <- df.abiotic %>% left_join(df.abiotic.2)  %>% 
  mutate(Plot = NAAM %>% factor, X = `X.coördinaat`, Y=`Y.coördinaat`) %>%
  group_by(Plot) %>% filter(DATE == max(DATE)) %>% filter(releve_nr != 203857) #NAAM = nb1019 has two releve_nr in same year
```

@@

```{r}
NL <- (NL - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
```

>>>>

## Original LMF data set to LMF subset
Here as well as in the modelling code, all coordinates are in EPSG:28992 Projected coordinate system for Netherlands.

@@

```{r}
# Abiotic measurements for LMF data 
LMF.dir <- file.path('LMF', 'LMF data.xlsx')
df.abiotic <- read_excel(LMF.dir, 1)[-1,-1] %>% distinct(releve_nr, .keep_all=T) %>% 
  mutate(across(DATE:`N-(NO3+NO2)`,as.numeric)) %>% mutate(NAAM=tolower(str_replace_all(NAAM, " ", "")))
# Fix some identifier names in abiotic data
naam <- df.abiotic$NAAM
# some FR**** and FR**** identifiers were not properly zero padded
replace.index <- substr(naam,1,2) %in% c("fr", "fl")
pad.4 <- paste(substr(naam,1,2), str_pad(substr(naam,3,nchar(naam)), 4, pad="0"), sep="")
df.abiotic[replace.index, "NAAM"] <- pad.4[replace.index]
# Some GR**** identifiers were GR****/GR****
replace.index <- grepl('/', df.abiotic$NAAM, fixed = TRUE)
last.6 <- substr(naam, nchar(naam)-6+1, nchar(naam))
df.abiotic[replace.index, "NAAM"] <- last.6[replace.index]
# Lisa's fixes to coordinates 
# This consisted of 24 plots of which the locations seemed to be outside of the Netherlands. The plotnames were found in the LMF plots, and for those the correct coordinates were taken from the LMF programme. 
# There were also an additional 329 abiotic plots with a plot name that was in the LMF file, but where the coordinates did not match. In those cases the coordinates from the LMF programme were taken as well. 
# Tostrams, Lisa <lisa.tostrams@rivm.nl>
df.abiotic.2 <- read.csv('LMF/lmf_log_data_corrected_coords.csv') %>% 
  distinct(releve_nr, .keep_all=T) %>% 
  select(releve_nr, `X.coördinaat`, `Y.coördinaat`)
# Replace coordinates
df.abiotic <- df.abiotic %>% left_join(df.abiotic.2)  %>% 
  mutate(Plot = NAAM %>% factor, X = `X.coördinaat`, Y=`Y.coördinaat`) %>%
  group_by(Plot) %>% filter(DATE == max(DATE)) %>% filter(releve_nr != 203857) #NAAM = nb1019 has two releve_nr in same year
```

@@

```{r}
NL <- st_read("data_paper/NL.shp")$geometry
NL <- (NL - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
```
